Tunable Spectral Ordering of Magnetic Plasmon Resonances

### 2018-04-05 paper_winter_2017/draft_winter_2017.tex

Most crucial to this disconnect is the question of when and how retardation effects matter. For example, in the case of the two oligomer cluster (the 2-mer) the quasistatic approximation has been shown to deviate from full-wave numerical electrodynamics simulations in that it predicts a different energy-ordering of the magnetic plasmon resonances.\cite{Cherqui2014}. Retardation effects have been incorporated into models of single MNPs\cite{Gu2010}, dimers\cite{Oubre2004,vonPlessen2007}, and infinite chains and arrays\cite{Lucas1976,ARAVIND1981,Kottman2001,NordHal2003,NordProdan2004,Rechbacher2003,Schatz2003,Royer2005,Abajo2008,Gomez2009,Chumanov2010,Pinchuk2016}. However, with the exception of numerical studies, no analytical models include retardation effects in the description of magnetic plasmon oligomers. Here, we show that the incorporation of retardation effects corrects the aforementioned discrepancy between model and simulation, and further points to the facile ability to tune the magnetic plasmon spectrum via scaling oligomer size. This is important because it allows for the facile manipulation of the effective permittivity and permeability thereby facilitating the design of future tunable optical metamaterials.

@@

\begin{figure}
\includegraphics{CL_incomplete.pdf}
\caption{Angle-resolved cathodoluminescence spectra of the 2mer (a and b) and 3mer (c and d). By choosing the beam positions marked on the diagrams and choosing different angles at which to measure the light emitted, the magnetic modes of each oligomer can be disentangled. The colored "x's" correspond to colored traces. The blue traces show a collection angle of $\phi = 3\pi/2$ and the orange traces are for $\phi = \pi$, while both have $\theta = \pi/4$. Simulating these CL experiments with $r_0 = 15$ nm shows the aN modes lower in energy than the NS modes, as predicted. WIth $r_0 = 30$ nm, the modes switch, again as predicted.}
\label{CL_2mer_3mer}
\end{figure}

>>>>

Most crucial to this disconnect is the question of when and how retardation effects matter. For example, in the case of the two oligomer cluster (the 2-mer) the quasistatic approximation has been shown to deviate from full-wave numerical electrodynamics simulations in that it predicts a different energy-ordering of the magnetic plasmon resonances.\cite{Cherqui2014} Retardation effects have been incorporated into models of single MNPs\cite{Gu2010}, dimers\cite{Oubre2004,vonPlessen2007}, and infinite chains and arrays\cite{Lucas1976,ARAVIND1981,Kottman2001,NordHal2003,NordProdan2004,Rechbacher2003,Schatz2003,Royer2005,Abajo2008,Gomez2009,Chumanov2010,Pinchuk2016}. However, with the exception of numerical studies, no analytical models include retardation effects in the description of magnetic plasmon oligomers. Here, we show that the incorporation of retardation effects corrects the aforementioned discrepancy between model and simulation, and further points to the facile ability to tune the magnetic plasmon spectrum via scaling oligomer size. This is important because it allows for the facile manipulation of the effective permittivity and permeability thereby facilitating the design of future tunable optical metamaterials.

@@

\begin{figure}
\includegraphics{CL_incomplete.pdf}
\caption{Angle-resolved cathodoluminescence spectra of the 2mer (a and b) and 3mer (c and d). By choosing the beam positions marked on the diagrams and choosing different angles at which to measure the light emitted, the magnetic modes of each oligomer can be disentangled. The colored "x's" correspond to colored traces. The blue traces show a collection angle of $\phi = 3\pi/2$ and the orange traces are for $\phi = \pi$, while both have $\theta = \pi/4$. Simulating these CL experiments with $r_0 = 15$ nm shows the aN modes lower in energy than the NS modes, as predicted. With $r_0 = 30$ nm, the modes switch, again as predicted.}
\label{CL_2mer_3mer}
\end{figure}
